Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-16 vesicle_code/docs/adhesion/adhesion.tex
yny changed extensional section

The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on a
planar extensional flow  where the fluid velocity field $\uu=\chi(-x,y)$ is centered at the 
the origin ($(x,y)=(0,0)$), the stagnation point where the fluid flow converges horizontally and diverges vertically.
Placed symmetrically at the stagnation point of an extensional flow,
a single vesicle may remain steady and symmetric for low extension rate $\chi$.
For sufficiently large extension rate $\chi$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}, 
similar to a surfactant-laden viscous drop under a planar extensional flow \cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.

To investigate how two vesicles interact with each other in a planar extensional flow,
at the beginning of the simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
we place a vesicle at $(x,y)=(0,0)$, 
and the other vesicle at $(x,y) = (3,\triangle y)$ where the initial vertical displacement $\triangle y$ varies from
$\triangle y=0$ for the top row, $\triangle y = 0.02$ for the second row, to
$\triangle y =0.1$ for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.

Once the planar extensional flow is turned on at $t=0^+$, two vesicles move
towards each other  as shown in  Figure \ref{fig:extensionalNonsymmetric}.
For $\triangle y=0$ in the top row, the two vesicles stay on the $x$-axis as they move closer to 
form a doublet. We observe that the left vesicle (initially centered at $(0,0)$) moves to the left due to the impinging
vesicle from the right. As time progresses they form a doublet
and reach a steady configuration that is symmetric with respect to the stagnation point 
(square mark in Figure \ref{fig:extensionalNonsymmetric}).

@@

Results in Figure~\ref{fig:extensionalNonsymmetric} illustrate that
in an extensional flow vesicles are prone to move away from the stagnation point:
A small initial vertical displacement $\triangle y$ in one  of the vesicles causes both vesicles to not only rotate but also move away from the
center. Once vesicles move off the horizontal axis, their hydrodynamics is dominated by the diverging flow as they move further away.
Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
%
With an active
control algorithm to place the stagnation point at a desirable location
by adjusting the flow with a feedback
loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle can be trapped at the
stagnation point for long time scales to facilitate image acquisition or
other detailed measures such as particle image velocimetry of flow
inside and around the particle.

>>>>

The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on a
planar extensional flow  where the fluid velocity field $\uu=\chi(-x,y)$ is centered at the 
the origin ($(x,y)=(0,0)$), the stagnation point where the fluid flow converges horizontally and diverges vertically.
Placed symmetrically at the stagnation point of an extensional flow,
a single vesicle may remain steady and symmetric for low extension rate $\chi$.
For sufficiently large extension rate $\chi$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}, 
similar to a surfactant-laden viscous drop under a planar extensional flow \cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.
To our knowledge no studies on the interactions between two vesicles in an extensional flow are available in the literature.
In the following we first illustrate how two vesicles interact with each other in a planar extensional flow. We then illustrate how the adhesion strength between membranes can be
measured non-intrusively by using the fluid trap.

%To investigate how two vesicles interact with each other in a planar extensional flow,
At the beginning of the first set of simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
we place a vesicle at $(x,y)=(0,0)$, 
and the other vesicle at $(x,y) = (3,\triangle y)$ where the initial vertical displacement $\triangle y$ varies from
$\triangle y=0$ for the top row, $\triangle y = 0.02$ for the second row, to
$\triangle y =0.1$ for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
The color coding is the membrane tension with the color bar on the right of each row.

Once the planar extensional flow is turned on at $t=0^+$, two vesicles move
towards each other  as shown in  Figure \ref{fig:extensionalNonsymmetric}.
For $\triangle y=0$ in the top row, the two vesicles stay on the $x$-axis as they move closer to 
form a doublet. We observe that the left vesicle (initially centered at $(0,0)$) moves to the left due to the impinging
vesicle from the right. As time progresses they form a doublet
and reach a steady configuration that is symmetric with respect to the stagnation point 
(square marks in the top row of Figure \ref{fig:extensionalNonsymmetric}).

@@

Two main observations can be made of results in Figure~\ref{fig:extensionalNonsymmetric}:
(1) The membrane tension is highly non-uniform on the vesicles, leading to a significant Marangoni stress along the membrane as in the case of a surfactant-laden drop
at the center of an extensional flow. Thus it is reasonable to expect that the flow around the vesicles is significantly altered.
(2) In an extensional flow vesicles are prone to move away from the stagnation point.
A small initial vertical displacement $\triangle y$ in one  of the vesicles causes both vesicles to not only rotate but also move away from the
center. Once vesicles move off the horizontal axis, their hydrodynamics is dominated by the diverging flow as they move further away.
Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
%
With an active
control algorithm to place the stagnation point at a desirable location
by adjusting the flow with a feedback
loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle can be trapped at the
stagnation point for long time scales to facilitate image acquisition or
other detailed measures such as particle image velocimetry of flow
inside and around the particle.
